A Triple Origin for Twin Blue Stragglers in Compact Binaries

### 2018-12-27 BSS7782.tex
corrected minor typo

The stellar-evolution model, its structure, temperature and
composition profiles are turned into a smoothed-particles
representation using the module {\tt StellarModelInSPH} in AMUSE (see
chapter 4 in \cite{AMUSE}).  We follow the same procedure as described
in \cite{2014MNRAS.438.1909D} for simulating the future of the triple
system \chi Tau (HD 97131) in which the outer-most star overfills it
Roche lobe to an inner binary.  After generating the hydrodynamical
representation of the donor star we replace the stellar core by a
point mass to prevent the majority of the resolution to be confined in
the star's central region.  In a following step we relax the star
using the hydrodynamics solver. This relaxation process is realized in
100 steps during which we reduce the velocity dispersion of individual
SPH particles to a glasseas structure \citep[see, for example, \S\,3.3
  on page 40 in][]{1994astro.ph.10043W}. During this procedure the
gaseous envelope of the star tends to expand by about 20\%.  To
detemrine the radius of the eventual star we calculate Lagrangian
radii and use the distance to the stellar center which contains 90\%
of it's mass. This 90\% mass-radius we consider as the stellar radius,
and match it with the Roche-lobe of the outer orbit.

>>>>

The stellar-evolution model, its structure, temperature and
composition profiles are turned into a smoothed-particles
representation using the module {\tt StellarModelInSPH} in AMUSE (see
chapter 4 in \cite{AMUSE}).  We follow the same procedure as described
in \cite{2014MNRAS.438.1909D} for simulating the future of the triple
system \xi Tau (HD 97131) in which the outer-most star overfills it
Roche lobe to an inner binary.  After generating the hydrodynamical
representation of the donor star we replace the stellar core by a
point mass to prevent the majority of the resolution to be confined in
the star's central region.  In a following step we relax the star
using the hydrodynamics solver. This relaxation process is realized in
100 steps during which we reduce the velocity dispersion of individual
SPH particles to a glasseas structure \citep[see, for example, \S\,3.3
  on page 40 in][]{1994astro.ph.10043W}. During this procedure the
gaseous envelope of the star tends to expand by about 20\%.  To
detemrine the radius of the eventual star we calculate Lagrangian
radii and use the distance to the stellar center which contains 90\%
of it's mass. This 90\% mass-radius we consider as the stellar radius,
and match it with the Roche-lobe of the outer orbit.
